---
title: "Homework #5"
author: "Sophia Miller"
date: "11/3/2019"
output: github_document
---
```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
library(broom)
library(viridis)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

# Problem 1

First, we will load the `iris` dataset and introduce missing values in each column: 

```{r iris}
set.seed(10)
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

The function below replaces missing values according to the following rules:

* For numeric variables, missing values are filled in with the mean of non-missing values
* For character values, missing values are filled in with `"virginica"`

```{r replace_missing_function}
replace_missing = function(x) {
  
   if (is.numeric(x)) {
    ifelse(is.na(x), mean(x, na.rm = TRUE), x)
   } else if (is.character(x)) {
     ifelse(is.na(x), "virginica", x)
   }
     
}

iris_complete = map_df(iris_with_missing, replace_missing)
```

# Problem 2

In this problem, we are creating a tidy data frame containing data from 20 csv files from a longitudinal study (10 control participants and 10 experimental participants) and plotting observations for each subject over time

```{r list_files, message = FALSE}
read_data = function(path) {
  df = read_csv(path)
  df
}

directory_base = "./data/"

complete = tibble(
  participant = list.files(path = "./data"), 
  values = str_c(directory_base, participant)) %>% 
    mutate(
    data = (map(values, read_data))) %>%
  unnest(cols = data) %>% 
  pivot_longer(
    week_1:week_8, 
    names_to = "week",
    values_to = "value") %>% 
  separate(participant, c("arm", "id")) %>% 
  separate(week, c("week_label", "week")) %>% 
  select(-values, -week_label) %>% 
  mutate(
    id = as.numeric(id),
    week = as.numeric(week),
    arm = recode(arm, con = "Control", exp = "Experimental" ))

complete = as.data.frame(complete)

ggplot(complete, aes(x = week, y = value)) +
geom_point(aes(group = id, color = arm)) +
geom_path(aes(color = arm)) +
labs(
    title = "Observations Over Time",
    x = "Week",
    y = "Observation",
    color = "Study Arm") +
theme(plot.title = element_text(hjust = 0.5))
```

As we can see from the plot above, the behavior of observations over time varies by study arm. At week 1, the observations for both arms are similar. However, the observations in the experimental arm increase over the course of the eight weeks, where as the observations in the control arm appear to remain similar over time.

# Problem 3

Here, we run a simluation to explore power: 

```{r regression, cache = TRUE}
sim_regression = function(n = 30, beta0 = 2, beta1 = 0) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 50^0.50)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  tidy(ls_fit) %>% 
    filter(term == "x")

}

#run function for beta1 = 0 first
sim_results = 
  rerun(100, sim_regression()) %>% 
  bind_rows

#now run function for beta1 = 0,1,2,3,4,5,6
sim_results1 = 
  tibble(
    beta1 = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_list = map(.x = beta1, ~rerun(100, sim_regression(beta1 = .x))),
    estimate_dfs = map(output_list, bind_rows)) %>% 
  select(-output_list) %>% 
  unnest(estimate_dfs)
```

```{r}
sim_results1 %>% 
  mutate(
    reject = ifelse(p.value <= 0.05, "significant", "non-significant")
    ) %>%
  group_by(beta1, reject) %>% 
  mutate(
    significant_count = n()
    ) %>% 
  mutate(significant_rate = significant_count/10000) %>%
  select(beta1, significant_rate) %>% 
  filter(reject == "significant") %>% 
  distinct(.keep_all = TRUE) %>%
  ggplot(aes(x = beta1, y = significant_rate)) + 
  geom_col(aes(fill = "viridis"), show.legend = FALSE) +
  labs(
    title = "Power vs. True Value of Beta1",
    x = "Beta 1",
    y = "Power",
    fill = " "
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

Plotting average estimate of beta 1 vs. true value of beta 1

```{r prob3_second_plot}
sim_results1 %>%
  group_by(beta1) %>% 
  summarize(mean_estimate = mean(estimate)) %>%
  ggplot(aes(x = beta1, y = mean_estimate)) +
  geom_col(aes(fill = "viridis"), show.legend = FALSE) +
  labs(
    title = "Average Estimate of Beta 1 vs. True Value of Beta 1",
    x = "Beta 1",
    y = "Average Estimate of Beta 1",
    fill = " "
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

Plotting average estimate of beta 1 vs. true value of beta 1 for samples where null was rejected:

```{r}
sim_results1 %>% 
  mutate(reject = ifelse(p.value <= 0.05, "significant", "non-significant")) %>%
  filter(reject == "significant") %>% 
  group_by(beta1) %>% 
  summarize(mean_estimate = mean(estimate)) %>%
  ggplot(aes(x = beta1, y = mean_estimate)) +
  geom_col(aes(fill = "viridis"), show.legend = FALSE) +
  labs(
    title = "Average Estimate of Beta 1 vs. True Value of Beta 1, When Null was Rejected",
    x = "Beta 1",
    y = "Average Estimate of Beta 1",
    fill = " "
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

